Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-24 paper.tex
Updated Experiment
Improved experiment description.

>>>>

            The third experiment objective was to confirm Animal Life Cycle
            Algorithm continued finding solutions in a reduced number of
            evaluations. For this test, we selected the Griewank Benchmark
            Function for Optimization. Figure~\ref{fig.fun_griewank} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Table~\ref{tab.fun_griewank5} and
            Table~\ref{tab.fun_griewank10} (for five and ten dimensions,
            respectively). With this analysis, we confirmed our strategy
            continued to obtain solutions in the same order as expected, in a
            reduced number of evaluations, in less time.
